Supplement 6

### 2023-04-18 Code/Manuscript_figures.Rmd
cleaned up code

library(tidyverse)
library(tidytext)
library(ggrepel)

@@

setwd("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts")
cut_date <-as.Date("2021-12-21")

### Need functions
source("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Code/Inc_Case_Eval_Manuscript/coverage.R") #coverage

@@

```{r Fig1, echo=FALSE, warning=F, message=F, fig.height=6.5, fig.width=6.5}
### Reported cases over time
source("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Code/Inc_Case_Eval_Manuscript/reported cases.R") #reported cases
obs_data <-rd_obs() %>%
  filter(nchar(location) < 3) %>%
  filter(date <= (cut_date+4)+(7*3)) %>%
  mutate(true_value=ifelse(true_value <=0, NA, true_value),
         true_value.pop=ifelse(is.na(true_value), NA, true_value.pop))

@@

load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata")

@@

mean_WIS <-function() {
  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_nat_state.rdata")

@@

  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_2021-03-13.Rdata")
  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_2022-03-21.Rdata")

@@

# Figures
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata")

@@

# Largest Counties
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata")
coverage_count <-cov.fig_dat(filter(dat_large_count, sub_date <= cut_date))
labels_count <-data_labels(coverage_count) 
Cov.Co <-cov.plot(coverage_count, labels_count) +
  labs(title="C. Coverage for Large County Forecasts*",
       x="Expected Coverage")

@@

  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_large counties.rdata")

@@

  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_non large counties_all.Rdata")
  rel_WIS_co <-WIS_all %>%
    ungroup() %>%
    summarise_scores(by = c("model", "pop_size_quant2"),
                     metric="interval_score",
                     relative_skill = TRUE,
                     baseline = "COVIDhub-baseline") %>%
    dplyr::select(model, scaled_rel_skill, pop_size_quant2) %>%
    mutate(geo_scale=ifelse(pop_size_quant2==1, "County Forecasts: Size Quantile 1 (Smallest)",
                            ifelse(pop_size_quant2==2, "County Forecasts: Size Quantile 2",
                                   ifelse(pop_size_quant2==3, "County Forecasts: Size Quantile 3", "County Forecasts: Size Quantile 4" 
                                          #"County forecasts: Size Quantile 5 (Largest)"
                                          )))) %>%
    dplyr::select(-pop_size_quant2) %>%
    bind_rows(., rel_WIS_large_co)
}
relWIS_co <-relWIS_co()
models_include_co <-relWIS_co %>%
  filter(geo_scale=="County Forecasts: Size Quantile 1 (Smallest)") %>%
  dplyr::select(model, geo_scale) %>%
  distinct()

@@

# Forecasts
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_nat_state.Rdata")

@@

### WIS Over time
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_nat_state.Rdata")

@@

## Large Counties
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_large counties.Rdata")
WIS_ot_co <-WIS.ot.fig_dat(WIS_all)
Fig6.C <-ot.plot(WIS_ot_co, date, abWIS) +
  labs(title = "C. Average Weighted Interval Score for Large County Forecasts*",
       x = "Forecast target date",
       y = "Average Weighted Interval Score") + theme(axis.text.y=element_text(angle=90, vjust=0.5, hjust=0.5)) +
  scale_y_continuous(trans='log10')

@@

load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata")
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata")

@@

load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_gee.Rdata") # data
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/gee_for_manuscript.rda")

@@

# Figure
Fig7A <-marg_means_int %>%
  ggplot(.) +
  geom_point(aes(model, predicted_back_rescale)) +
  geom_linerange(aes(model, ymin=predicted_back_lo_rescale, ymax=predicted_back_up_rescale)) +
  geom_hline(data=baseline, mapping=aes(yintercept=baseline$predicted_back_lo_rescale), color="red", linetype="dashed") + 
  geom_hline(data=baseline, mapping=aes(yintercept=baseline$predicted_back_up_rescale), color="red", linetype="dashed") +
  labs( y="Marginal mean\n Weighted Interval Score", 
        title="A.") +
  theme_bw() +
  theme(axis.title.y=axis.title.y_standard, axis.text=axis.text_standard,
        legend.position = "bottom", legend.title = element_blank(), legend.text=legend.text_standard,
        strip.text=strip.text_standard, strip.background=strip.background_standard,
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust=1))

@@

Fig7A_updated <-Fig7A + theme(axis.text.x = element_blank())

plot_grid(Fig7A_updated, Fig7B, rel_heights  = c(0.5, 1), axis = "l",
          align="v", nrow = 2)

>>>>

library(here)
library(tidyverse)
library(tidytext)
library(ggrepel)

@@

cut_date <-as.Date("2021-12-21")

### Need functions
source(here("Code/coverage.R")) #coverage

@@

```{r Fig1, echo=FALSE, warning=F, message=F, fig.height=6.5, fig.width=6.5}
### Reported cases over time
source(here("Code/Reported cases.R")) #reported cases
obs_data <-rd_obs() %>%
  filter(nchar(location) < 3) %>%
  filter(date <= (cut_date+4)+(7*3)) %>%
  mutate(true_value=ifelse(true_value <=0, NA, true_value),
         true_value.pop=ifelse(is.na(true_value), NA, true_value.pop))

@@

load(here("Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata"))

@@

mean_WIS <-function() {
  load(here("Data/WIS_all horizons_nat_state.rdata"))

@@

  load(here("Data/cases_nat_state_forecasts_2021-03-13.Rdata"))
  load(here("Data/cases_nat_state_forecasts_2022-03-21.Rdata"))

@@

# Figures
load(here("Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata"))

@@

# Largest Counties
load(here("Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata"))
coverage_count <-cov.fig_dat(filter(dat_large_count, sub_date <= cut_date))
labels_count <-data_labels(coverage_count) 
Cov.Co <-cov.plot(coverage_count, labels_count) +
  labs(title="C. Coverage for Large County Forecasts*",
       x="Expected Coverage")

@@

  load(here("Data/WIS_all horizons_large counties.Rdata"))

@@

  load(here("Data/WIS_all horizons_non large counties_all.Rdata"))
  rel_WIS_co <-WIS_all %>%
    ungroup() %>%
    summarise_scores(by = c("model", "pop_size_quant2"),
                     metric="interval_score",
                     relative_skill = TRUE,
                     baseline = "COVIDhub-baseline") %>%
    dplyr::select(model, scaled_rel_skill, pop_size_quant2) %>%
    mutate(geo_scale=ifelse(pop_size_quant2==1, "County Forecasts: Size Quantile 1 (Smallest)",
                            ifelse(pop_size_quant2==2, "County Forecasts: Size Quantile 2",
                                   ifelse(pop_size_quant2==3, "County Forecasts: Size Quantile 3", "County Forecasts: Size Quantile 4" 
                                          #"County forecasts: Size Quantile 5 (Largest)"
                                          )))) %>%
    dplyr::select(-pop_size_quant2) %>%
    bind_rows(., rel_WIS_large_co)
}
relWIS_co <-relWIS_co()
models_include_co <-relWIS_co %>%
  filter(geo_scale=="County Forecasts: Size Quantile 1 (Smallest)") %>%
  dplyr::select(model, geo_scale) %>%
  distinct()

@@

# Forecasts
load(here("Data/WIS_all horizons_nat_state.Rdata"))

@@

### WIS Over time
load(here("Data/WIS_all horizons_nat_state.Rdata"))

@@

## Large Counties
load(here("Data/WIS_all horizons_large counties.Rdata"))
WIS_ot_co <-WIS.ot.fig_dat(WIS_all)
Fig6.C <-ot.plot(WIS_ot_co, date, abWIS) +
  labs(title = "C. Average Weighted Interval Score for Large County Forecasts*",
       x = "Forecast target date",
       y = "Average Weighted Interval Score") + theme(axis.text.y=element_text(angle=90, vjust=0.5, hjust=0.5)) +
  scale_y_continuous(trans='log10')

@@

load(here("Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata"))
load(here("Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata"))

@@

load(here("Data/WIS_gee.Rdata")) # data
load(here("Data/gee_for_manuscript.rda"))

@@

# Figure
Fig7A <-marg_means_int %>%
  ggplot(.) +
  geom_point(aes(model, predicted_back_rescale)) +
  geom_linerange(aes(model, ymin=predicted_back_lo_rescale, ymax=predicted_back_up_rescale)) +
  geom_hline(data=baseline, mapping=aes(yintercept=baseline$predicted_back_lo_rescale), color="red", linetype="dashed") + 
  geom_hline(data=baseline, mapping=aes(yintercept=baseline$predicted_back_up_rescale), color="red", linetype="dashed") +
  labs( y="Marginal mean\n Weighted Interval Score", 
        title="A.") +
  theme_bw() +
  theme(axis.title.y=axis.title.y_standard, axis.text.y=axis.text_standard,
        legend.position = "bottom", legend.title = element_blank(), legend.text=legend.text_standard,
        strip.text=strip.text_standard, strip.background=strip.background_standard,
        axis.title.x = element_blank(),
        #axis.text.x = element_text(angle = 45, hjust=1),
        axis.text.x = element_blank())

@@

plot_grid(Fig7A, Fig7B, rel_heights  = c(0.5, 1), axis = "l",
          align="v", nrow = 2)

### 2023-04-18 Code/Supplement 1B_figures.Rmd
cleaned up code

setwd("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts")

@@

####
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_county_forecasts_2022-04-04.Rdata")
size <-read.csv("C:/Users/oko8/Downloads/SVI2018_US_COUNTY.csv") %>%
  dplyr::select(FIPS, E_TOTPOP) %>%
  rename(location=FIPS) %>%
  mutate(location=as.character(location),
         location=ifelse(nchar(location)==4, paste0("0", location), location),
         pop_size_quant2=cut(E_TOTPOP, breaks = quantile(E_TOTPOP, probs = seq(0, 1, 0.20)),
                             include.lowest = TRUE, labels = 1:5)
  ) %>% 
  dplyr::select(-E_TOTPOP) 
all_dat <-all_dat %>% left_join(., size, by="location") 
rm(size)
counts <-all_dat %>%
  filter(!(model %in% sec_models),
         sub_date >= start_date & sub_date <= stop_date) %>%
  filter(type=="point")

>>>>

@@

####
load(here("Data/cases_county_forecasts_2022-04-04.Rdata"))
size <-read.csv(here("Data/SVI2018_US_COUNTY.csv")) %>%
  dplyr::select(FIPS, E_TOTPOP) %>%
  rename(location=FIPS) %>%
  mutate(location=as.character(location),
         location=ifelse(nchar(location)==4, paste0("0", location), location),
         pop_size_quant2=cut(E_TOTPOP, breaks = quantile(E_TOTPOP, probs = seq(0, 1, 0.20)),
                             include.lowest = TRUE, labels = 1:5)
  ) %>% 
  dplyr::select(-E_TOTPOP) 
all_dat <-all_dat %>% left_join(., size, by="location") 
rm(size)
counts <-all_dat %>%
  filter(!(model %in% sec_models),
         sub_date >= start_date & sub_date <= stop_date) %>%
  filter(type=="point")

### 2023-04-18 Code/Supplement 2_Outliers.Rmd
cleaned up code

library(tidyverse)
library(covidcast)
library(epiprocess)

@@

## rename locations based on state names
states <-read.csv("C:/Users/oko8/OneDrive - CDC/Projects/covid19-forecast-hub/data-locations/locations.csv") %>%
  rename(fips = location) %>%
  mutate(fips = as.character(fips)) %>%
  filter(nchar(fips)==2) %>%
  dplyr::select(abbreviation, location_name)

@@

## Read in data
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_gee.Rdata")

>>>>

library(here)
library(tidyverse)
library(covidcast)
library(epiprocess)

@@

## rename locations based on state names
states <-read.csv(here("Data/locations.csv")) %>%
  rename(fips = location) %>%
  mutate(fips = as.character(fips)) %>%
  filter(nchar(fips)==2) %>%
  dplyr::select(abbreviation, location_name)

@@

## Read in data
load(here("Data/WIS_gee.Rdata"))

### 2023-04-18 Code/Supplement 3.1_figure.rmd
cleaned up code

setwd("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts")

### Need functions
source("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Code/Inc_Case_Eval_Manuscript/coverage.R") #coverage

@@

mean_WIS <-function() {
  ## Large counties
  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_large counties.rdata")

@@

  ## Non Large counties
  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_non large counties_all subs.rdata")

@@

cov.95 <-function() {
  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata")

@@

  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_non large counties_forecasts_for analysis_2022-08-18.Rdata")

@@

load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata")
subs_co <-submissions(df=dat_large_count) %>%
  mutate(pop_size_quant2="County Forecasts: Size Quantile 5")

load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_non large counties_forecasts_for analysis_2022-08-18.Rdata")
subs_co_other <-submissions(df=dat_other_count) %>%
  rename_counts()

>>>>

### Need functions
source(here("Code/coverage.R")) #coverage

@@

mean_WIS <-function() {
  ## Large counties
  load(here("Data/WIS_all horizons_large counties.rdata"))

@@

  ## Non Large counties
  load(here("Data/WIS_all horizons_non large counties_all subs.rdata"))

@@

cov.95 <-function() {
  load(here("Data/cases_large counties_forecasts_for analysis_2022-08-18.rdata"))

@@

  load(here("Data/cases_non large counties_forecasts_for analysis_2022-08-18.rdata"))

@@

load(here("Data/cases_large counties_forecasts_for analysis_2022-08-18.rdata"))
subs_co <-submissions(df=dat_large_count) %>%
  mutate(pop_size_quant2="County Forecasts: Size Quantile 5")

load(here("Data/cases_non large counties_forecasts_for analysis_2022-08-18.rdata"))
subs_co_other <-submissions(df=dat_other_count) %>%
  rename_counts()

### 2023-04-18 Code/Supplement 5_all figures.Rmd
updated figures after coauthor review
cleaned up code

load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata")

@@

# Largest Counties
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata")
coverage_count <-cov.fig_dat(filter(dat_large_count, sub_date <= cut_date,
                                   !grepl("2", target),
                                   !grepl("3", target)))
labels_count <-data_labels(coverage_count) 
Cov.Co <-cov.plot(coverage_count, labels_count) +
  facet_wrap(~target) +
  theme(strip.text=strip.text_standard, strip.background=strip.background_standard) +
  labs(title="C. Coverage for Large County Forecasts*",
       x="Expected Coverage")

@@

### WIS Over time
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_nat_state.Rdata")

@@

## Large Counties
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_large counties.Rdata")
WIS_ot_co <-WIS.ot.fig_dat(filter(WIS_all, 
                                  !grepl("2", target),
                                  !grepl("3", target))) 
Fig2.D <-ot.plot(WIS_ot_co, date, abWIS) +
  facet_wrap(~ target) +
  theme(strip.text=strip.text_standard, strip.background=strip.background_standard) +
  scale_y_continuous(trans='log10') +
  labs(title = "C. Average Weighted Interval Score for Large County Forecasts*",
       x = "Forecast target date",
       y = "Average Weighted Interval Score") + 
  theme(axis.text.y=element_text(angle=90, vjust=0.5, hjust=0.5))

@@

load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata")
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata")

@@

```{r Fig S5.3, echo=FALSE, warning=FALSE, message=FALSE, fig.height=10, fig.width=12.5}

# Forecasts
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_nat_state.Rdata")

>>>>

load(here("Data/cases_nat_state_forecasts_for analysis_2022-08-18.rdata"))

@@

# Largest Counties
load(here("Data/cases_large counties_forecasts_for analysis_2022-08-18.rdata"))
coverage_count <-cov.fig_dat(filter(dat_large_count, sub_date <= cut_date,
                                   !grepl("2", target),
                                   !grepl("3", target)))
labels_count <-data_labels(coverage_count) 
Cov.Co <-cov.plot(coverage_count, labels_count) +
  facet_wrap(~target) +
  theme(strip.text=strip.text_standard, strip.background=strip.background_standard) +
  labs(title="C. Coverage for Large County Forecasts*",
       x="Expected Coverage")

@@

### WIS Over time
load(here("Data/WIS_all horizons_nat_state.rdata"))

@@

## Large Counties
load(here("Data/WIS_all horizons_large counties.rdata"))
WIS_ot_co <-WIS.ot.fig_dat(filter(WIS_all, 
                                  !grepl("2", target),
                                  !grepl("3", target))) 
Fig2.D <-ot.plot(WIS_ot_co, date, abWIS) +
  facet_wrap(~ target) +
  theme(strip.text=strip.text_standard, strip.background=strip.background_standard) +
  scale_y_continuous(trans='log10') +
  labs(title = "C. Average Weighted Interval Score for Large County Forecasts*",
       x = "Forecast target date",
       y = "Average Weighted Interval Score") + 
  theme(axis.text.y=element_text(angle=90, vjust=0.5, hjust=0.5))

@@

load(here("Data/cases_nat_state_forecasts_for analysis_2022-08-18.rdata"))
load(here("Data/cases_large counties_forecasts_for analysis_2022-08-18.rdata"))

@@

```{r Fig S5.3, echo=FALSE, warning=FALSE, message=FALSE, fig.height=10, fig.width=15}

# Forecasts
load(here("Data/WIS_all horizons_nat_state.rdata"))

### 2023-04-18 Code/Supplement 6_figures.Rmd
cleaned up code

load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_gee.Rdata") # data
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Code/model_caseslogstd_noint_gee.rda")

WIS_gee <-WIS_gee %>%
  group_by(model) %>%
  mutate(WIS_log_std=(log(interval_score)-mean(log(interval_score)))/sd(log(interval_score)),
         cases_log_std=(log(true_value)-mean(log(true_value)))/sd(log(true_value))
  ) %>%
  ungroup()

@@

  marg_means[[i]] <-ggemmeans(model[[i]], terms=c("phase_all", "cases_log_std[-1.96:1.96]")) %>%
    rename(phase_all=x,
           cases=group) %>% 
    mutate(model=team[i],
           predicted_back=(predicted*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
           predicted_back_lo=(conf.low*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
           predicted_back_up=(conf.high*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
           cases=as.numeric(as.character(cases)),
           cases_log_back=(cases*means_sds[[i]]$sd_log_cases) + means_sds[[i]]$mean_log_cases) %>%
    mutate(predicted_back_rescale=exp(predicted_back),
           predicted_back_lo_rescale=exp(predicted_back_lo),
           predicted_back_up_rescale=exp(predicted_back_up),
           cases_back_rescale=exp(cases_log_back))
}
marg_means <-do.call(rbind.data.frame, marg_means)

@@

  mutate(model=as.factor(model)) %>%
  mutate(phase_all=as.factor(ifelse(phase_all=="increasing", "Increasing",
                                    ifelse(phase_all=="decreasing", "Decreasing",
                                           ifelse(phase_all=="peak", "Peak", "Nadir")))),
         phase_all=factor(phase_all, 
                          levels = c("Increasing", "Peak", "Decreasing",  "Nadir"))
  )

# Figure
FigS6 <-marg_means %>%
  ggplot(., aes(cases_back_rescale, predicted_back_rescale)) +
  geom_line(aes(color=phase_all)) +
  geom_ribbon(aes(ymin=predicted_back_lo_rescale, ymax=predicted_back_up_rescale, fill=phase_all), alpha=0.35) +
  scale_fill_manual(breaks = c("Increasing", "Decreasing", "Unclassified", "Peak", "Nadir"), 
                      values=c("#fdae61", "#abdda4", "#bababa", "#d7191c", "#2b83ba")) +
  scale_color_manual(breaks = c("Increasing", "Decreasing", "Unclassified", "Peak", "Nadir"), 
                      values=c("#fdae61", "#abdda4", "#bababa", "#d7191c", "#2b83ba")) +
  labs( y="Marginal Mean \nWeighted Interval Score", x="Reported cases") +
  facet_wrap(~model) +
  theme_bw() +
  theme(axis.title.y=axis.title.y_standard,
        legend.title = element_blank(), legend.text=legend.text_standard,
        strip.text=strip.text_standard, strip.background=strip.background_standard,
        axis.text.x = element_text(angle = 45, hjust=1)) +
  guides(fill=guide_legend(nrow=2, byrow=TRUE))

>>>>

load(here("./Data/WIS_gee.Rdata")) # data
load(here("./Data/gee_for_manuscript.rda"))

@@

  marg_means[[i]] <-ggemmeans(model[[i]], terms=c("phase", "cases_log_std[-1.96:1.96]")) %>%
    rename(phase=x,
           cases=group) %>% 
    mutate(model=team[i],
           predicted_back=(predicted*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
           predicted_back_lo=(conf.low*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
           predicted_back_up=(conf.high*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
           cases=as.numeric(as.character(cases)),
           cases_log_back=(cases*means_sds[[i]]$sd_log_cases) + means_sds[[i]]$mean_log_cases) %>%
    mutate(predicted_back_rescale=exp(predicted_back),
           predicted_back_lo_rescale=exp(predicted_back_lo),
           predicted_back_up_rescale=exp(predicted_back_up),
           cases_back_rescale=exp(cases_log_back))
}
marg_means <-do.call(rbind.data.frame, marg_means)

@@

  mutate(model=as.factor(model)) %>%
  mutate(phase=as.factor(ifelse(phase=="increasing", "Increasing",
                                    ifelse(phase=="decreasing", "Decreasing",
                                           ifelse(phase=="peak", "Peak", "Nadir")))),
         phase=factor(phase, 
                          levels = c("Increasing", "Peak", "Decreasing",  "Nadir"))
  )

# Figure
FigS6 <-marg_means %>%
  ggplot(., aes(cases_back_rescale, predicted_back_rescale)) +
  geom_line(aes(color=phase)) +
  geom_ribbon(aes(ymin=predicted_back_lo_rescale, ymax=predicted_back_up_rescale, fill=phase), alpha=0.35) +
  scale_fill_manual(breaks = c("Increasing", "Decreasing", "Unclassified", "Peak", "Nadir"), 
                      values=c("#fdae61", "#abdda4", "#bababa", "#d7191c", "#2b83ba")) +
  scale_color_manual(breaks = c("Increasing", "Decreasing", "Unclassified", "Peak", "Nadir"), 
                      values=c("#fdae61", "#abdda4", "#bababa", "#d7191c", "#2b83ba")) +
  labs( y="Marginal Mean \nWeighted Interval Score", x="Reported cases") +
  facet_wrap(~model) +
  theme_bw() +
  theme(axis.title.y=axis.title.y_standard,
        legend.title = element_blank(), legend.text=legend.text_standard,
        strip.text=strip.text_standard, strip.background=strip.background_standard,
        axis.text.x = element_text(angle = 45, hjust=1)) +
  guides(fill=guide_legend(nrow=2, byrow=TRUE))
